
% License : MIT
%------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\begin{center}
    {\Huge \scshape ANUBHAV ANAND} \\ \vspace{2pt}
    \small \raisebox{-0.1\height}\faPhone\ +919304082618 ~ \href{mailto:anandanubhav1516@gmail.com}{\raisebox{-0.1\height}\faEnvelope\  {anandanubhav1516@gmail.com}} ~ 
    % \href{https://meyash.xyz}{\raisebox{-0.1\height}\faLink\ {meyash.xyz}} ~
    \href{www.linkedin.com/in/anandanubhav1516}{\raisebox{-0.1\height}\faLinkedin\ {Linkedln}}  ~
    \href{https://github.com/anubhavanand1516}{\raisebox{-0.2\height}\faGithub\ {Github}}
    \vspace{-8pt}
\end{center}

\vspace{} % Hacky fix for awkward extra vertical space
%-----------EXPERIENCE-----------
\section{Work Experience}
    \resumeSubheading
      {\href{https://feynnlabs.com/}{Feynn Labs}}{April 2022 – June 2022}
      {Machine Learning Intern}{Guwahati, Assam}
      \resumeItemListStart
      \resumeItem{working on client project on the B2B segment.}
        \resumeItem{with the help of Machine Learning solutions using machine learning tools we can, record and analyze calls. Based on the analysis, the algorithm can transcribe and highlight areas where customers have mentioned pain points, competitor’s name, pricing and so on.}
      \resumeItemListEnd
    
    \resumeSubheading
       {\href{https://www.madrasresearch.org/}{Madras Scientific Research Foundation}}{March 2022 – May 2022}
      {Machine Learning Intern}{Chennai, Tamil Nadu}
      \resumeItemListStart
        \resumeItem{working on research project.}
        \resumeItem{The main theme of the project,we have to turning photographs into artwork with Neural Style Transfer and deep learning.}
    \resumeItemListEnd
    
    \resumeSubheading
         {\href{https://www.suvidhafoundation.org/}{Suvidha Foundation}}{January 2022 – March 2022}
      {Machine Learning Intern.}{Nagpur, Maharashtra}
      \resumeItemListStart
        \resumeItem{ Our Project was on the viedo summarization, in this project we have to abstract the feature from the large viedo using
framework and algorithms(RCNN,LSTM), we have to detect the any obstacles in the viedo and then we have to compress
into small viedo.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
% \vspace{-13pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
        \resumeProjectHeading
          {\textbf{Pose Detection} $|$ \emph{ Python, React.js, mediapipe, CNN}}{\href{https://github.com/anubhavanand1516/pose_detection_Rootally}{Github}}
          \resumeItemListStart
            \resumeItem{Developed an multiple pose detection using mediapipe framework, apply some hand engineering and do some modification so that it vetorize the each sigement body parts  precisely.CNN are used to extract the features.}
              \resumeItem{This technology are used in medical field,robotics to find there accurate posture of the body.}
          \resumeItemListEnd 
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Real Time Helmet Detection} $|$ \emph{ Python, YOLO , CNN }}{\href{https://github.com/anubhavanand1516/Artenal_assignment-}{Github}}
          \resumeItemListStart
            \resumeItem{ Developed an Helmet Detection and trained it on a wide variety of helmet so that it can achieved a high accuracy,in this
project we used YOLO framework.}
            \resumeItem{ We used YOLO algorithm because it has high inference speed and also detection of small or far objects.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
% \vspace{-15pt}
  %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Poornima College of Engineering}{2020 - 2024}
      {Bachelor of technology (B.tech) in Computer Engineering, CGPA: 8.56(till 2nd sem)}{Jaipur, Rajasthan}
  \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
    \resumeSubheading
      {Sardar Patel Public School}{2018 - 2019}
      {12th, percentage: 76.6}{Bokaro steel city, Jharkhand}
  \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
    \resumeSubheading
      {Sardar Patel Public School}{2018 - 2022}
      {10th, CGPA: 10}{Bokaro steel city, Jharkhand}
  \resumeSubHeadingListEnd
 
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{:  C, C++, Python, JavaScript,HTML,Machine learning,Computer vision} \\
     \textbf{Databases}{: SQL, MongoDB } \\
     \textbf{Libraries / Frameworks}{:  Node.js, React.js,Tensorflow} \\
     \textbf{Tools / Platforms}{:  Git, Gitlab, Linux, Heroku,FastAPI} \\
     \textbf{Coursework}{: Data Structures, Algorithms, OS, DBMS, Computer Networks} \\
    }}
 \end{itemize}
%-----------INVOLVEMENT---------------
\section{Achievements}
    \resumeSubHeadingListStart
            \resumeItemListStart
                \resumeItem{ I have secured two times winner at Child Right Congress(State Level).}
                \resumeItem{I have secured two times winner at National Children Science Congress(National Level)}
                \resumeItem{ I have received an intern offer letter from an HCL technology.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
© 2022 GitHub, Inc.
Terms
Privacy
Security
Status
Docs
Contact GitHub
Pricing
API
Training
Blog
About